Instant Continuation Marks--Just Add $\lambda$

### 2012-10-02 paper.tex
Direct style.

\begin{schemedefn}{\scheme|C[(rator-expr rand-expr)]|}
\begin{schemedisplay}
(lambda (kont)
   (lambda (flag)
     (lambda (marks)
       (((C[rator-expr]
          (lambda (rator-value)
            (((C[rand-expr]
               (lambda (rand-value)
                 ((((rator-value rand-value) kont) flag) marks)))
              FALSE)
             m)))
         FALSE)
        m))))
\end{schemedisplay}
\end{schemedefn}

@@

\begin{schemedefn}{\scheme|C[(wcm mark-expr body-expr)]|}
\begin{schemedisplay}
(lambda (kont)
  (lambda (flag)
    (lambda (marks)
      (((C[mark-expr]
         (lambda (mark-value) ((lambda (k_1) 
                                 (k_1 (((marks (lambda (x) x)) (lambda (z) z)) (lambda (z) z))))
                               (lambda (t) 
                                 ((lambda (k_2) (k_2 ((f C[(SND t)]) t)))
                                   (lambda (rest) 
                                     (((C[body-expr] kont) TRUE) C[(CONS mark-value rest)])))))))
        FALSE)
       marks))))
\end{schemedisplay}
\end{schemedefn}

@@

\begin{schemedefn}{\scheme|C[(ccm)]|}
\begin{schemedisplay}
(lambda (kont)
  (lambda (flag)
    (lambda (marks)
      (((marks kont) (lambda (z) z)) (lambda (z) z)))))
\end{schemedisplay}
\end{schemedefn}

>>>>

\begin{schemedefn}{\scheme|C[(rator-expr rand-expr)]|}
\begin{schemedisplay}
(lambda (flags)
  (lambda (marks)
    (((((C[rator-expr] FALSE) marks)
       ((C[rand-expr] FALSE) marks))
      flags)
     marks)))
\end{schemedisplay}
\end{schemedefn}

@@

\begin{schemedefn}{\scheme|C[(wcm mark-expr body-expr)]|}
\begin{schemedisplay}
(lambda (flag)
  (lambda (marks)
    ((C[body-expr] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       ((C[mark-expr] FALSE) marks))
      ((flag ((C[(SND marks)] (lambda (z) z)) (lambda (z) z))) marks)))))
\end{schemedisplay}
\end{schemedefn}

@@

\begin{schemedefn}{\scheme|C[(ccm)]|}
\begin{schemedisplay}
(lambda (flag)
  (lambda (marks)
    marks))
\end{schemedisplay}
\end{schemedefn}
